---
title: "ANA 515 Assignment 4"
author: "Gyu Hyun Byun"
date: "2022-10-15"
output: word_document
---

```{r setup, include=FALSE}
library(dplyr)
library(tidyverse)
library(scales)
```

# 1. Discuss the business problem/goal 
The goal is to recognize fraudulent credit card transactions so that customers are not charged for items that they did not purchase.

# 2. Identify where the dataset was retrieved from
The dataset was retrieved from https://www.kaggle.com/datasets/mlg-ulb/creditcardfraud?resource=download

# 3. Identify the code that imported and saved your dataset in R
The dataset is saved as "creditcard_raw".

```{r data, include = TRUE}
setwd("/Users/Qram/OneDrive/Documents/McDaniel/ANA 515 Fundamentals of Data Storage/Week 8")
creditcard_raw <- read.csv("creditcard.csv")
```

# 4. Describe your data set

The original data has `r nrow(creditcard_raw)` rows and `r ncol(creditcard_raw)` columns. The names of the columns and a brief description of each are:

```{r, echo = TRUE}
names(creditcard_raw) #to show column names

#Time = Number of seconds elapsed between this transaction and the first transaction in the dataset
#V1 ~ V28 = may be result of a PCA Dimensionality reduction to protect user identities and sensitive features(V1-V28)
#Amount = Transaction amount
#Class = 1 for fraudulent transactions, 0 otherwise
```

# 5-8. Discuss any data preparation, missing values, errors, the modeling, and the output. Provide explanation with any visuals.

The dataset contains transactions made by credit cards in September 2013 by European cardholders.
This dataset presents transactions that occurred in two days, where we have `r sum(creditcard_raw$Class == "1")` frauds out of `r nrow(creditcard_raw)` transactions. The dataset is highly unbalanced, the positive class (frauds) account for `r percent(sum(creditcard_raw$Class == "1")/nrow(creditcard_raw), accuracy = 0.001)` of all transactions.

```{r, echo = TRUE}
sum(creditcard_raw$Class == "1") #to show the number of fraudulent transactions
nrow(creditcard_raw) #to show the number of total transactions
percent(sum(creditcard_raw$Class == "1")/nrow(creditcard_raw), accuracy = 0.001) #to show the % of fraudulent transactions
```



```{r, echo = TRUE}
creditcard_fraud <- creditcard_raw[creditcard_raw$Class == "1",] #to create a subdataset for fraudulent transactions
creditcard_nofraud <- creditcard_raw[creditcard_raw$Class == "0",] #to create a subdataset for non-fraudulent transactions

summary(creditcard_fraud$Amount) #to show the summary of the Amount variable of the fraudulent subdataset

summary(creditcard_nofraud$Amount) #to show the summary of the Amount variable of the non-fraudulent subdataset
```

Per the summaries above, we cannot seem to identify a notable difference in the Amount variable between the two subdataset.

Let's investigate further to determine if the Amount variable can help us tell fraudulent transactions from normal transactions.

```{r, echo = TRUE}
creditcard_raw$Fraud[creditcard_raw$Class == "1"] <- "Fraudulent" #to create a new variable, Fraud, and mark it "Fraudulent" if the transaction is classified as fraudulent per the Class variable.
creditcard_raw$Fraud[creditcard_raw$Class == "0"] <- "Non-Fraudulent" #to create a new variable, Fraud, and mark it "Non-Fraudulent" if the transaction is not classified as fraudulent per the Class variable.

ggplot(creditcard_raw, aes(x = Fraud, y = Amount)) + geom_boxplot() #to draw a graph to compare the transaction amounts between the two groups.
t.test(Amount ~ Fraud, data = creditcard_raw, var.equal = TRUE, paired = FALSE) #to perform a t-test to draw a conclusion.
```

Based on the boxplot and t-test performed above, the mean of the variable Amount is a good indicator of identifying fraudulent transactions as the p-value is only 0.002651.
